\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2023-03-01 R/Supp_Info_1.Rmd
Fixing problem with the axis in the plot

```{r}
my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 
                                                    5, 
                                                    15, 
                                                    26, 
                                                    30,
                                                    68, 
                                                    72, 
                                                    76,
                                                    80,
                                                    84,
                                                    94,
                                                    100)]

@@

plot_format <- "png"
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")

###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.5, 12.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab = "Technical Difficulty", 
      line = 4, 
      cex.lab = 1)
title(xlab = "Degree of Collaboration", 
      line = 3.5, 
      cex.lab = 1)

@@

text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nMembers", 
                "Other \nLabs", 
                "EEB \nCommunity", 
                "All \nUsers"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))

>>>>

```{r plot-segments}
my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 
                                                    5, 
                                                    15, 
                                                    26, 
                                                    30,
                                                    68, 
                                                    72, 
                                                    76,
                                                    80,
                                                    84,
                                                    94,
                                                    100)]

@@

plot_format <- "png"
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 600,
      bg = "white")  
}

par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty = "n")

###############################################################
# create the plot background
###############################################################

plot(x = c(0.5, 5.5),
     y = c(0.5, 12.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02,
     yaxt = "n"
     # yaxs = 'i'
     )

title(ylab = "Technical Difficulty", 
      line = 4, 
      cex.lab = 1)

title(xlab = "Degree of Collaboration", 
      line = 3.5, 
      cex.lab = 1)

@@

axis(2,
     seq(1, 12, length.out = 5),
     outer = F,
     labels = F,
     pos = 0.5,
     hadj = 1)

text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nMembers", 
                "Other \nLabs", 
                "EEB \nCommunity", 
                "All \nUsers"))

text(x = c(0.5, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
